My title

### 2023-03-15 outputs/paper/paper.qmd
Adding references to quarto document

Through examining the different relationships between the various variables and the weekly total number of hours of internet use, we found that those of young adults tend to use the internet more than older adults. This may be due to physical, psychological, and social barriers when using the internet. We also found that those who have never been married use the internet more than others with different marital statuses. This could be correlated with age and the difference in reasons for using the internet. Additionally, as social media is a large part of internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low internet usage and a high level of happiness.

Using the internet more regularly can improve the lives of individuals for its convenience and its accessibility. It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information.

@@

## Third discussion point {#sec-third-point}
In a previous study, we found a potential correlation between happiness and internet usage. Specifically, individuals who reported lower internet usage tended to have higher levels of happiness. There are few reasons may be contribute to this finding.

@@

### Weakness
A key weakness in our analysis was that we removed non-responses from our data, which may have made our data for Internet use not as accurate in reflecting what the actual population’s Internet use looks like. A central reason as to why participant’s may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question. This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern. (@cite26)

Another weakness in our analysis is the self-reported nature of the results, meaning there was some bias in questions with ambiguous word choice, such as our happiness variable. The definition of the different response options to the happiness variable survey question of “not so happy”, “fairly happy”, and “very happy” will vary depending on the individual, as well as the day or time of day. Thus, our analysis of the relationship between happiness and Internet use may be biased.

### Next Steps
To address our second identified weakness in Section 4.4.2 above, implementing a supplementary survey with more detailed questions, particularly about race and gender (as mentioned in Section 2.2) and more straightforward question answers (e.g. a number scale for happiness variable) would allow for more in-depth analysis.

>>>>

Through examining the different relationships between the various variables and the weekly total number of hours of internet use, we found that those of young adults tend to use the internet more than older adults. This may be due to physical, psychological, and social barriers when using the internet. We also found that those who have never been married use the internet more than others with different marital statuses. This could be correlated with age and the difference in reasons for using the internet. Additionally, as social media is a large part of internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low internet usage and a high level of happiness. Using the internet more regularly can improve the lives of individuals for its convenience and its accessibility. It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information \[**cite**\].

@@

## Third discussion point {#sec-third-point}

In a previous study, we found a potential correlation between happiness and internet usage. Specifically, individuals who reported lower internet usage tended to have higher levels of happiness. There are few reasons may be contribute to this finding.

@@

### Weakness

A key weakness in our analysis was that we removed non-responses from our data, which may have made our data for Internet use not as accurate in reflecting what the actual population's Internet use looks like. A central reason as to why participant's may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question. This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern. (@cite26)

Another weakness in our analysis is the self-reported nature of the results, meaning there was some bias in questions with ambiguous word choice, such as our happiness variable. The definition of the different response options to the happiness variable survey question of "not so happy", "fairly happy", and "very happy" will vary depending on the individual, as well as the day or time of day. Thus, our analysis of the relationship between happiness and Internet use may be biased.

### Next Steps

To address our second identified weakness in Section 4.4.2 above, implementing a supplementary survey with more detailed questions, particularly about race and gender (as mentioned in Section 2.2) and more straightforward question answers (e.g. a number scale for happiness variable) would allow for more in-depth analysis.
